Marine Conservation and Fishing Effort Markets[^*]

### 2019-05-14 docs/slides/NCEAS_presentation.Rmd
Added and updated slides for NCEAS presentation last week

---
title: "Marine Conservation and Fishing Effort Markets"
author:
  - Villaseñor-Derbez J.C.$^1$
  - Lynham J.$^2$
  - Costello C.$^{1, 3}$
institute: 
   - $^1$Bren School, UCSB
   - $^2$Department of Economics, UHM
   - $^3$emLAB, UCSB
subtitle: "NCEAS-Future Earth Working Group"
date: "May 6, 2019"
output: 
  beamer_presentation: 
    theme: Darmstadt
header-includes:
  - \usepackage{media9}
---

@@

  - Phoenix Island Protected Area

@@

@@

# PIPA

@@

- ~2\% of total PNA area

- ~10\% of fishing activity in PNA

@@

- Devideded into three groups

## Two fleets

@@

## Effort displacement

@@

## Effort displacement raster

```{r}
knitr::include_graphics(here("docs", "img", "rasterized_change.png"))
```

# Extra slides - GFW data

@@

## Vessel statistics

A short table with information on number of vessels per year and class

Palau-specific information about longliners

>>>>

---
title: "Marine Conservation and Fishing Effort Markets[^*]"
author:
  - Villaseñor-Derbez J.C.$^1$
  - Lynham J.$^2$
  - Costello C.$^{1, 3}$
institute: 
   - $^1$Bren School, UCSB
   - $^2$Department of Economics, UHM
   - $^3$emLAB, UCSB
subtitle: "NCEAS-Future Earth Working Group"
date: "May 6, 2019"
output: 
  beamer_presentation: 
    theme: Darmstadt
header-includes:
  - \usepackage{media9}
  - \usepackage{eso-pic,graphicx,transparent}
---

[^*]: This is work in progress developed for the NCEAS working group. Please do not share externally. Results are yet to be refined and peer-reviewed.

\AddToShipoutPictureFG{
  \AtPageCenter{% or \AtTextCenter
    \makebox[0pt]{\rotatebox[origin=c]{45}{%
      \scalebox{5}{\texttransparent{0.3}{DRAFT}}%
    }}
  }
}

@@

  - Phoenix Island Protected Area*

@@

### Effort displacement by large-scale MPAs

- Where was effort displaced to?

- Does effort displacement imply revenue losses from VDS?

- Does a 30\% closure mean a 30\% loss in revenue?

@@

## Palau Vessel-day schemes

- Purse seine vessel-days

  - 700 purse seine vessel-days

  - \$5.60 - \$8.75 Million USD

  - Tradable

  - Trading might reduce costs, but allocation rules matter

- Longline vessel-days

  - 10,500 longline vessel-days

  - \$2.10 Million USD

  - Non-tradable

## Conclusions

- Under no trading, implementing a reserve is costly

  - More fish movement reduces costs

- Trading lessens the blow of a spatial closure

  - \% costs avoided by trading decrease as biomass in implementing patch increases

- Allocation rules matter

  - A biomass-based allocation ($\alpha = 0$) reduces long-term costs

# Extra slides

## GFW summary for Palau

```{r}
knitr::include_graphics(here("docs", "slides", "img", "vessels_in_plw.png"))
```

@@

- 2.7\% of total PNA area

- 11\% of Kiribati EEZ

- 22\% of Kiribati EEZ (excluding Line Islands)

@@

- 2012 - Present

## Two "fleets"

@@

@@

## Effort displacement in all PNA

## Displaced vessels

```{r}
knitr::include_graphics(here("docs", "img", "fishing_raster_displaced.png"))
```

## Non-displaced vessels

```{r}
knitr::include_graphics(here("docs", "img", "fishing_raster_not_displaced.png"))
```

## Difference

```{r}
knitr::include_graphics(here("docs", "img", "fishing_raster_difference_between_groups.png"))
```

# GFW Data

@@
